Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-07 windheat.tex
More modifications to the appendix.

\begin{align}
  \dot{m}(\Mstar)=8 \times 10^{-14} \frac{L_* R_*}{\Mstar}
  \left(\frac{T_{\rm eff}}{\rm 4000 K}\right)^{3.5}
  \left(1+\frac{g_{\odot}}{4300 g_*}\right) \Msun \pyear,\
\end{align}

@@

To get a handle on $\dot{e}_{\rm TO}(t)$, we use the results from
\citet{VossDiehl+:2009a} who use a population synthesis code to
simulate the mass and energy injection into the ISM from an OB
association. For the first $\sim 10$ Myr the energy injection will
come from energetic Wolf-Rayet star winds. The energy injection rate
per massive star ($\Mstar>8 \Msun$), $\dot{\mathcal{E}} (t)$, from
stellar winds is plotted in the top panel of their Figure 7 and is
well fit {\bf AG: A little more detail here...} by

@@

@@

where $f_{8}$ is the fraction of the stellar population with
$\Mstar>8 \Msun$. $f_8=2.6 \times 10^{-3}$ for our assumed Salpeter
IMF.  Equation~\eqref{eq:voss} and~\eqref{eq:eto} will be valid onlyfor $t
\lsim 10$ Myr. However, the turnoff contribution will become extremely
energetically subdominant at later times as far slower dust-driven
winds come to dominate the energy budget {\bf AG: Nick check--is the
  preceding sentence accurate}

@@

We plot $\bar{v}_w$ in Figure~\ref{fig:vwImp}.

>>>>

\begin{align}
  \dot{m}(\Mstar)=8 \times 10^{-14} \frac{L_* r_*}{\Mstar}
  \left(\frac{T_{\rm eff}}{\rm 4000 K}\right)^{3.5}
  \left(1+\frac{g_{\odot}}{4300 g_*}\right) \Msun \pyear,\
\end{align}

@@

To get a handle on $\dot{e}_{\rm TO}(t)$, we use the results from
\citet{VossDiehl+:2009a} who use a population synthesis code to
simulate the mass and energy injection into the ISM from an OB
association. For the first $\sim 10$ Myr the energy injection will
be dominated by fast Wolf-Rayet star winds. The energy injection rate
per massive star ($\Mstar>8 \Msun$), $\dot{\mathcal{E}} (t)$, from
stellar winds is plotted in the top panel of their Figure 7 and is
well fit {\bf AG: A little more detail here...} by

@@

Equation~\eqref{eq:voss} is valid only for $t \lsim 10$ Myr. For $t\gsim
10$ Myr, $\dot{e}_{\rm TO}$ will be negligible as lower mass stars
shed their gas is slow dust-driven winds during their post-main
sequence evolution {\bf AG-Nick is the preceding statement accurate},
and for our purposes the exact functional form of $\dot{e}_{\rm
  TO}(t)$ is unimportant. So we adopt Equation~\eqref{eq:voss} for all times.

@@

where $f_{8}$ is the fraction of the stellar population with $\Mstar>8
\Msun$. $f_8=2.6 \times 10^{-3}$ for our assumed Salpeter IMF.

@@

We plot $\bar{v}_w$ versus time in Figure~\ref{fig:vwImp}.
